---
title: "Follow Up Survey"
output: github_document
---

1. 無理に前提を置く必要はない。

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr)
library(ggplot2)
library(readr)
library(stringr)
library(tidyr)
source("script/subject_info.R")
```

```{r}
results <- read_csv("follow-up.csv")
View(results)
```

```{r}
item_list <- read_csv("../src/list/axb_list.csv") %>%
  select(c(item_id, type, condition, correct, item_a, item_x, item_b, c1, c2))
subject_info_sone <- read_csv("csv/illusory-vowel-keihan.csv") %>%
  extract_columns(data_src = "sone")
subject_info_cw <- read_csv("csv/illusory-vowel-keihan-cw.csv") %>%
  extract_columns(data_src = "cw")
# ここの input_id で合わせればいい
subject_info <- rbind(subject_info_sone, subject_info_cw)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


